Comparison of Catalogs

### 2024-07-24 compare/compare.qmd
SFR+Masses

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support
#quantity_support()
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import glob
import os
plt.style.use('ggplot')

@@

The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)`

@@

|      LCV      |          HECATE          |                        Description                        | Pearson Correlation \[-1,1\] |
|:---------------:|:---------------:|:------------------:|:---------------:|
|     TType     |     T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
|      inc      |           INCL           |                     Inclination (deg)                     |     `{python} inc_corr`      |
| a26_1 (Major) | A26_1a (Semi-major axis) |                 angular diameter (arcmin)                 |     `{python} a26_corr`      |

@@

```{python}
#| echo: false
logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"])[3], 3)
```

@@

```{python}
#| echo: false
mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"], sigma = True)[3], 3)
Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], unc = dt["E_K"])[3], 3)
```

|         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
|:---------------:|:-------------:|:-------------:|:------------------------:|
| mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
|        Kmag         |        K         | 2MASS band magnitude (both) |     `{python} Kmag_corr`     |

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:-----------:|:-----------:|:----------------------------:|:---------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |

@@

|  LCV   |   HECATE   |                           Description                            |
|:------------------:|:------------------:|:------------------------------:|
|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] |
|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  |
|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      |
|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      |
|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      |
|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   |
|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        |
| SFRFUV |            |             FUV derived integral star formation rate             |
| SFRHa  |            |          H{alpha} derived integral star formation rate           |

@@

|      LCV       |  HECATE  |                        Description                        |
|:------------------:|:------------------:|:------------------------------:|
|     logM26     |          |              Log mass within Holmberg radius              |
|     logMHI     |          |              Log mass within Holmberg radius              |
|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       |
|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] |
| logStellarMass |          |                Stellar Mass from M\*/L=0.6                |
:::

>>>>

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support
#quantity_support()
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')

@@

The dataset we are going to use consists of `{python} len(dt)` galaxies and `{python} len(dt.colnames)` columns.

@@

|      LCV      |          HECATE          |                        Description                        | Pearson Correlation \[-1,1\] |
|:----------------:|:----------------:|:------------------:|:----------------:|
|     TType     |     T (with errors)      | Numerical Hubble type following the de Vaucouleurs system |    `{python} ttype_corr`     |
|      inc      |           INCL           |                     Inclination (deg)                     |     `{python} inc_corr`      |
| a26_1 (Major) | A26_1a (Semi-major axis) |                 angular diameter (arcmin)                 |     `{python} a26_corr`      |

@@

```{python}
#| echo: false
logKLum_corr = round(compare_data(dt["logKLum"], dt["logL_K"], sigma = True)[3], 3)
```

@@

```{python}
#| echo: false
mag_B_corr = round(compare_data(dt["mag_B"], dt["BT"],unc = dt["E_BT"], sigma = False)[3], 3)
Kmag_corr = round(compare_data(dt["Kmag"], dt["K"], unc = dt["E_K"])[3], 3)
```

|         LCV         |      HECATE      |         Description         | Pearson Correlation \[-1,1\] |
|:--------------:|:--------------:|:--------------:|:----------------------:|
| mag_B (with errors) | BT (with errors) |                             |    `{python} mag_B_corr`     |
|        Kmag         |        K         | 2MASS band magnitude (both) |     `{python} Kmag_corr`     |

@@

|  LCV   | HECATE |                  Description                   | Pearson Correlation \[-1,1\] |
|:--------------:|:--------------:|:------------------------:|:--------------:|
|   AB   |   AG   |    Galactic extinction/absorption in B band    |      `{python} ab_corr`      |
| AB_int |   AI   | Internal/Intrisic B band extinction/absorption |              0               |

@@

```{python}
#| echo: false
# Extract the relevant SFR columns
sfr_columns = ["logSFR_TIR", "logSFR_FIR", "logSFR_60u", "logSFR_12u", "logSFR_22u", "logSFR_HEC", "logSFR_GSW", "logSFRFUV", "logSFRHa"]
sfr_data = dt[sfr_columns].to_pandas()

# Count the number of non-NaN cells for each column
non_nan_counts = sfr_data.notna().sum()
```

|  LCV   |   HECATE   |                           Description                            |                  Count                  |
|:--------------:|:--------------:|:------------------------:|:--------------:|
|        | logSFR_TIR | Decimal logarithm of the total-infrared SFR estimate \[Msol/yr\] | `{python} non_nan_counts["logSFR_TIR"]` |
|        | logSFR_FIR |  Decimal logarithm of the far-infrared SFR estimate \[Msol/yr\]  | `{python} non_nan_counts["logSFR_FIR"]` |
|        | logSFR_60u |      Decimal logarithm of the 60um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_60u"]` |
|        | logSFR_12u |      Decimal logarithm of the 12um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_12u"]` |
|        | logSFR_22u |      Decimal logarithm of the 22um SFR estimate \[Msol/yr\]      | `{python} non_nan_counts["logSFR_22u"]` |
|        | logSFR_HEC |  Decimal logarithm of the homogenised SFR estimate \[Msol/yr\]   | `{python} non_nan_counts["logSFR_HEC"]` |
|        | logSFR_GSW |       Decimal logarithm of the SFR in GSWLC-2 \[Msol/yr\]        | `{python} non_nan_counts["logSFR_GSW"]` |
| SFRFUV |            |             FUV derived integral star formation rate             | `{python} non_nan_counts["logSFRFUV"]`  |
| SFRHa  |            |          H{alpha} derived integral star formation rate           |  `{python} non_nan_counts["logSFRHa"]`  |

```{python}
#| echo: false
sfr_data.drop("logSFR_GSW", axis=1, inplace=True)
# Compute the correlation matrix
corr_matrix = sfr_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of SFR Values")
plt.show()

# Create a pair grid
sns.pairplot(sfr_data)
plt.show()

It is possible we dont see a correlation because we dont have a big enough common sample

@@

```{python}
#| echo: false
# Extract the relevant mass columns
mass_columns = ["logM26", "logMHI", "logM_HEC", "logM_GSW", "logStellarMass"]
mass_data = dt[mass_columns].to_pandas()

# Count the number of non-NaN cells for each column
non_nan_counts = mass_data.notna().sum()
```

|      LCV       |  HECATE  |                        Description                        |                  Count                  |
|:------------------:|:------------------:|:------------------------------:|:------------------------------:|
|     logM26     |          |              Log mass within Holmberg radius              | `{python} non_nan_counts["logM26"]`     |
|     logMHI     |          |              Log mass within Holmberg radius              | `{python} non_nan_counts["logMHI"]`     |
|                | logM_HEC |      Decimal logarithm of the stellar mass \[Msol\]       | `{python} non_nan_counts["logM_HEC"]`   |
|                | logM_GSW | Decimal logarithm of the stellar mass in GSWLC-2 \[Msol\] | `{python} non_nan_counts["logM_GSW"]`   |
| logStellarMass |          |                Stellar Mass from M_*/L=0.6                | `{python} non_nan_counts["logStellarMass"]` |

```{python}
#| echo: false
mass_data.drop("logM_GSW", axis=1, inplace=True)
# Compute the correlation matrix
mass_corr_matrix = mass_data.corr()

# Create a heatmap
plt.figure(figsize=(10, 8))
sns.heatmap(mass_corr_matrix, annot=True, cmap="coolwarm", vmin=-1, vmax=1)
plt.title("Correlation Heatmap of Mass Values")
plt.show()

# Create a pair grid
sns.pairplot(mass_data)
plt.show()
```

:::
